DeepSphere: a graph-based spherical CNN

### 2019-09-23 main.tex
spectrum (SHREC17 and cosmo)

\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\usepackage{booktabs}
\usepackage{bbm}        % for mathbbm
\usepackage{graphicx} \graphicspath{{figures/}}
%\usepackage{wrapfig}
\usepackage{floatflt}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

@@

\begin{floatingfigure}[r]{0.5\linewidth}
%\begin{wrapfigure}{r}{0.5\linewidth}
	\centering
	\includegraphics[height=6em]{lamp_000018}
	\includegraphics[height=6em]{lamp_000018_sphere_nobar}
	\caption{Example of a 3D object represented as a spherical depth map. T}
	\label{fig:depthmap}
%\end{wrapfigure}
\end{floatingfigure}

@@

Results are shown in \tabref{shrec17}.
DeepSphere achieves the same performance as \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} while being much more efficient, suggesting that anisotropic filters are an unnecessary price to pay.
% x times faster
As the information in those spherical maps resides in the low frequencies (\todo{figure}), reducing the equivariance error didn't translate into improved performance.
For the same reason, using the more uniform HEALPix discretization or lowering the resolution down to $N_{side} = 8$ didn't impact performance.
\todo{The same conclusions are drawn from ModelNet 40 (see appendix ??).}

>>>>

\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\usepackage{booktabs}
\usepackage{bbm}        % for mathbbm
\usepackage{graphicx} \graphicspath{{figures/}}
%\usepackage{wrapfig}
%\usepackage{floatflt}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

@@

\begin{figure}
%\begin{floatingfigure}[r]{0.5\linewidth}
%\begin{wrapfigure}{r}{0.5\linewidth}
	\begin{minipage}[t]{0.57\linewidth}
		\centering
		\includegraphics[height=7em]{lamp_000018}
		\hfill
		\includegraphics[height=7em]{lamp_000018_sphere_nobar}
		\caption{Example of a 3D object represented as a spherical depth map.}
		\label{fig:depthmap}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.35\linewidth}
		\centering
		\includegraphics[height=7em]{spectrum}
		\caption{Power spectral densities.}
		\label{fig:spectrum}
	\end{minipage}
%\end{wrapfigure}
%\end{floatingfigure}
\end{figure}

@@

Results are shown in \tabref{shrec17}.
DeepSphere achieves the same performance as \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} while being much more efficient, suggesting that anisotropic filters are an unnecessary price to pay.
% x times faster
As the information in those spherical maps resides in the low frequencies (\figref{spectrum}), reducing the equivariance error didn't translate into improved performance.
For the same reason, using the more uniform HEALPix discretization or lowering the resolution down to $N_{side} = 8$ didn't impact performance.
\todo{The same conclusions are drawn from ModelNet 40 (see appendix ??).}
